Summer 2025 ToDo

### 2025-08-26 Relations/Paper/Summer_2025_TODO.tex
Changes from last meeting and minor edits.

\section*{20th August todos}
\begin{todolist}
  \item (Secondary) Find consistency with NP and UN with respect to reduction and conversion. Should the default be by reduction for both. Should we be explicit with $\to$ and = in each case. 
  \item Carry on modifying the names of wfXXX- to wfXXXnotnot with prefix underscore in agda and in latex.
  \item Make a decision regarding WFcor. We use it to imply WFacc using AccCor. But otherwise it is sort of orphaned off. Does it help contribute to the overall story?
\end{todolist}

>>>>

\section*{20th August todos}
\begin{todolist}
  \item (Secondary) Find consistency with NP and UN with respect to reduction and conversion. Should the default be by reduction for both. Should we be explicit with $\to$ and = in each case.  \sacomment{Main issue here is that we'll either introduce an inconsistency with our code or we'll have a hard to read symbol. We can do $\to$ as super or sub-script in Agda. If we're happy with $NP\to$ in agda but using a different script in the paper then I think we should go ahead and be explicit for both UN and NP as to whether it is WRT conversion or reduction. We already have this inconsistency in the code with $UN\to$} 
  \item Carry on modifying the names of wfXXX- to wfXXXnotnot with prefix underscore in agda and in latex. \sacomment{Done with the exception of WFseq-. This needs a bit more thought. Similarly for the relation between WFcor and WFminCor.}
  \item Make a decision regarding WFcor. We use it to imply WFacc using AccCor. But otherwise it is sort of orphaned off. Does it help contribute to the overall story? \sacomment{We've now related it to WFmin by requiring that correductive predicates have double negation elimination. Is this too strong a requirement? Similarly we have linked WFacc to WFcor but this proof requires the same property as well as limiting ourselves to accessible predicates. Again, is this too much?}
  \item Get the classical hypothesis and relations organized and see how they're used in the implications (organize implications by classical requirement. In the implications file we can import the classical implications. Basically, refactor the code.) \sacomment{Done but could be further refactored.}
  \item Make a cheat sheet for the next meeting regarding to talk about coreductive. How it relates on the weak side and on the strong side. SEQ seq+- , how to present these. Try and clarify what the issues are here and what exactly are the differences between them in terms of definition and implication. Could one be removed and the overall story stay the same? \sacomment{Regarding seq+ (and seq+-) we currently only show that seq+ implies seq and seq+- implies seq- so could be removed without changing any of our other implictions.}
\end{todolist}

### 2025-08-26 Relations/Paper/Well-foundedness.tex
Changes from last meeting and minor edits.

% Row 1: WFacc
\node[box] (WFacc) {WFacc};
% \node[box, right=of WFacc] (NNWFacc) {$\lnot\lnot$WFacc};
\node[box, right=2.9cm of WFacc] (WFaccM) {WFacc-};

@@

% Row 5: WFminDNE -> WFminDNE-
\node[box, below=of WFacc] (WFminDNE) {WFminDNE};
\node[box, right=2.0cm of WFminDNE] (WFminDNEM) {WFminDNE-};

@@

% Row 4: WFmin -> WFmin-
\node[box, below=of WFminDNE] (WFmin) {WFmin};
\node[box, right=2.8cm of WFmin] (WFminM) {WFmin-};

@@

% Row 3: WFseq
\node[box, below=of WFmin] (WFseq) {WFseq};
% \node[box, right=of WFseq] (NNWFseq) {$\lnot\lnot$WFseq};
\node[box, right=2.9cm of WFseq] (WFseqM) {WFseq-};

@@

% Row 6: WFcor 
\node[box, below=of WFseqM] (WFminCor) {WFminCor};

@@

\draw[arrow, bend right = 90] (WFacc) to node[left, text = red] {Rdec} (WFseq);
\draw[arrow, bend right] (WFaccM) to (WFminDNEM);
\draw[arrow, bend right = 90] (WFseqM) to node[right, text=red] {accCor} (WFaccM);  
% \draw[arrow, bend left = 55] (WFaccM) to (WFminM);

@@

\draw[arrow] (WFminDNE) to node[left, text = red] {accDNE} (WFacc);
\draw[arrow, bend right=45] (WFminDNE) to node[pos=0.5, left, text=red] {MP$\equiv$} (WFseq);
\draw[arrow, bend right] (WFminDNEM) to node[right, text=red] {FB} (WFaccM);
\draw[arrow, bend right] (WFseqM) to (WFminCor);
\draw[arrow, bend right] (WFminCor) to node [right, text=red] {MP$\equiv$} (WFseqM);

>>>>

% Row 1: WFacc
\node[box] (WFacc) {$WFacc$};
% \node[box, right=of WFacc] (NNWFacc) {$\lnot\lnot$WFacc};
\node[box, right=2.9cm of WFacc] (WFaccM) {$WFacc\lnot\lnot$};

@@

% Row 5: WFminDNE -> WFminDNE-
\node[box, below=of WFacc] (WFminDNE) {$WFminDNE$};
\node[box, right=2.0cm of WFminDNE] (WFminDNEM) {$WFminDNE\lnot\lnot$};

@@

% Row 4: WFmin -> WFmin-
\node[box, below=of WFminDNE] (WFmin) {$WFmin$};
\node[box, right=2.8cm of WFmin] (WFminM) {$WFmin\lnot\lnot$};

@@

% Row 3: WFseq
\node[box, below=of WFmin] (WFseq) {$WFseq$};
% \node[box, right=of WFseq] (NNWFseq) {$\lnot\lnot$WFseq};
\node[box, right=2.9cm of WFseq] (WFseqM) {$WFseq-$};

@@

% Row 6: WFcor 
\node[box, below=of WFseq] (WFCor) {$WFCor$};
\node[box, below=of WFseqM] (WFminCor) {$WFminCor$};

@@

\draw[arrow, bend right = 90] (WFacc) to node[pos = 0.75,left, text = red] {Rdec} (WFseq);
\draw[arrow, bend right] (WFaccM) to (WFminDNEM);
\draw[arrow, bend right = 90] (WFseqM) to node[right, text=red] {accCor} (WFaccM);  
% \draw[arrow, bend left = 55] (WFaccM) to (WFminM);

@@

\draw[arrow] (WFminDNE) to node[left, text = red] {accDNE} (WFacc);
\draw[arrow, bend right=45] (WFminDNE) to node[pos=0.5, left, text=red] {MP$\equiv$} (WFseq);
\draw[arrow, bend right] (WFminDNEM) to node[right, text=red] {FB} (WFaccM);
\draw[arrow, bend right] (WFseqM) to (WFminCor);
\draw[arrow, bend right] (WFminCor) to node [right, text=red] {MP$\equiv$} (WFseqM);
\draw[arrow] (WFCor) -- (WFminCor);
\draw[arrow, bend left = 110] (WFCor) to node[left, text=red] {AccCor} (WFacc);
